### 2014-10-24 ApTranscriptome_TR.Rmd

# A. carolinensis **Low** and **Bimodal**
md_sub1 <- subset(md, Acar %in% c("Low", "Bimodal", "High"), )
md_sub1 <- droplevels(md_sub1)

mh_plot_sub1 <- qplot(x=Apic, y=Acar, data=md_sub1, fill=value, geom="tile", ylim = rev(levels(md_sub1$Acar))) + 
  scale_fill_gradient2(limits=c(-600, 600)) +
  theme(axis.title = element_text(face="italic")) +
  labs(x = "A. picea", y = "A. carolinensis") +
  theme(legend.position = "bottom") + 
  geom_rect(xmin = 0.5, xmax = 1.5, ymin = 2.5, ymax = 3.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 2.5, xmax = 3.5, ymin = 1.5, ymax = 2.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 3.5, xmax = 4.5, ymin = .5, ymax = 1.5, fill = "transparent", linetype=2, colour="black")

@@

md_sub2 <- subset(md, Apic %in% c("Low", "High", "Bimodal"), )
md_sub2 <- droplevels(md_sub2)

mh_plot_sub2 <- qplot(x=Acar, y=Apic, data=md_sub2, fill=value, geom="tile", ylim = rev(levels(md_sub2$Apic))) + 
  scale_fill_gradient2(limits=c(-600, 600)) +
  theme(axis.title = element_text(face="italic")) +
  labs(x = "A. carolinensis", y = "A. picea") + 
  theme(legend.position = "none") + 
  geom_rect(xmin = 0.5, xmax = 1.5, ymin = 2.5, ymax = 3.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 2.5, xmax = 3.5, ymin = 1.5, ymax = 2.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 3.5, xmax = 4.5, ymin = 0.5, ymax = 1.5, fill = "transparent", linetype=2, colour="black")

@@

png("results/matched_observations_Fig1.png")
grid.arrange(mh_plot_sub2, mh_plot_sub1, ncol=1, heights = c(0.45, 0.6))
dev.off()

@@

# ratio of constitutive expression
Ap.response.type2.A22.high$Ar.A22.constitutive <- Ap.response.type2.A22.high$Ar.opt / Ap.response.type2.A22.high$A22.opt

# plot!
gg11 <- ggplot(Ap.response.type2.A22.high, aes(y = log(A22.Ar.upreg), x = log(Ar.A22.constitutive))) + 
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(y = expression(paste("log(inducibility ", italic("A. picea / A. carolinensis"), ")")),
       x = expression(paste("log(constitutive ", italic("A. carolinensis / A. picea"), ")")))

@@

A22.high.lm <- lm(log(A22.Ar.upreg) ~ log(Ar.A22.constitutive), data = Ap.response.type2.A22.high)

@@

# ratio of constitutive expression
Ap.response.type2.Ar.low$A22.Ar.constitutive <- Ap.response.type2.Ar.low$A22.opt / Ap.response.type2.Ar.low$Ar.opt

gg12 <- ggplot(Ap.response.type2.Ar.low, aes(y = log(Ar.A22.upreg), x = log(A22.Ar.constitutive))) + 
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(y = expression(paste("log(inducibility ", italic("A. carolinensis / A. picea"), ")")),
       x = expression(paste("log(constitutive ", italic("A. picea / A. carolinensis"), ")")))

@@

Ar.low.lm <- lm(log(Ar.A22.upreg) ~ log(A22.Ar.constitutive), data = Ap.response.type2.Ar.low)

@@

```{r fig2}
# add labels
gg11 <- gg11 + ggtitle('A') + theme(plot.title = element_text(hjust=0))
gg12 <- gg12 + ggtitle('B') + theme(plot.title = element_text(hjust=0))
# grid.arrange
png(file = "results/genetic_assimilation_Fig2.png")
grid.arrange(gg11, gg12, nrow = 1)
dev.off()
```

@@

png("results/crit_temp_regulation_Fig3.png")
grid.arrange(gg2, gg3, nrow = 2, heights = c(.5,.6))
dev.off()
```

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(TPM.dt.sub, RxNpval, sigtable, chi1, chi2, resp.TPM.dt.sub, Ap.type.table, tt2, tt3, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, w3, hsp_responsive, hsp_all, mh.test, mh_plot, Ap.BP.resultParentChild, resp.stress.responsive.count, T_on.high.ttest, T_on.low.ttest, T_off.int.high.ttest, T_off.int.low.ttest, Ap.gsea.intersect, Ar.int.A22.bim.gsea, Ar.int.A22.low.gsea, Ar.int.A22.lowbim.gsea, quadratic.lms, resp.TPM.dt.sub.pred, md, file = paste("doc/ms_", Sys.Date(), ".RData", sep = ""))
```

>>>>

# A. carolinensis **Low** and **Bimodal**
md_sub1 <- subset(md, Acar %in% c("Bimodal", "Low"), )
md_sub1 <- droplevels(md_sub1)

mh_plot_sub1 <- qplot(x=Apic, y=Acar, data=md_sub1, fill=value, geom="tile", ylim = rev(levels(md_sub1$Acar))) + 
  scale_fill_gradient2(limits=c(-600, 600)) +
  theme(axis.title = element_text(face="italic")) +
  labs(x = "A. picea", y = "A. carolinensis") +
  theme(legend.position = "none") + 
  geom_rect(xmin = 0.5, xmax = 1.5, ymin = 1.5, ymax = 2.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 3.5, xmax = 4.5, ymin = 0.5, ymax = 1.5, fill = "transparent", linetype=2, colour="black")

@@

# A. picea **High** and **Bimodal**
md_sub2 <- subset(md, Apic %in% c("High", "Bimodal"), )
md_sub2 <- droplevels(md_sub2)

mh_plot_sub2 <- qplot(x=Acar, y=Apic, data=md_sub2, fill=value, geom="tile", ylim = rev(levels(md_sub2$Apic))) + 
  scale_fill_gradient2(limits=c(-600, 600)) +
  theme(axis.title = element_text(face="italic")) +
  labs(x = "A. carolinensis", y = "A. picea") + 
  theme(legend.position = "bottom") + 
  geom_rect(xmin = 2.5, xmax = 3.5, ymin = 1.5, ymax = 2.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 3.5, xmax = 4.5, ymin = 0.5, ymax = 1.5, fill = "transparent", linetype=2, colour="black")

@@

png("results/matched_observations_Fig1.png")
grid.arrange(mh_plot_sub1, mh_plot_sub2, ncol=1, heights = c(0.45, 0.6))
dev.off()

@@

# ratio of constitutive expression
Ap.response.type2.A22.high$A22.Ar.constitutive <- Ap.response.type2.A22.high$A22.opt / Ap.response.type2.A22.high$Ar.opt

# plot!
gg11 <- ggplot(Ap.response.type2.A22.high, aes(x = log(A22.Ar.upreg), y = log(A22.Ar.constitutive))) + 
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(x = expression(paste("log(inducibility ", italic("A. picea / A. carolinensis"), ")")),
       y = expression(paste("log(constitutive expression ", italic("A. picea / A. carolinensis"), ")")))

@@

A22.high.lm <- lm(log(Ar.A22.constitutive) ~ log(A22.Ar.upreg), data = Ap.response.type2.A22.high)

@@

# ratio of constitutive expression
Ap.response.type2.Ar.low$Ar.A22.constitutive <- Ap.response.type2.Ar.low$Ar.opt / Ap.response.type2.Ar.low$A22.opt

gg12 <- ggplot(Ap.response.type2.Ar.low, aes(x = log(Ar.A22.upreg), y = log(Ar.A22.constitutive))) + 
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(x = expression(paste("log(inducibility ", italic("A. carolinensis / A. picea"), ")")),
       y = expression(paste("log(constitutive expression ", italic("A. carolinensis / A. picea"), ")")))

@@

Ar.low.lm <- lm(log(Ar.A22.constitutive) ~ log(Ar.A22.upreg), data = Ap.response.type2.Ar.low)

@@

```{r fig3}
# add labels
gg11 <- gg11 + ggtitle('A') + theme(plot.title = element_text(hjust=0))
gg12 <- gg12 + ggtitle('B') + theme(plot.title = element_text(hjust=0))
# grid.arrange
png(file = "results/genetic_assimilation_Fig3.png")
grid.arrange(gg11, gg12, nrow = 1)
dev.off()
```

@@

png("results/crit_temp_regulation_Fig2.png")
grid.arrange(gg2, gg3, nrow = 2, heights = c(.5,.6))
dev.off()
```

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(TPM.dt.sub, RxNpval, sigtable, chi1, chi2, chi3, chi4, chi5, resp.TPM.dt.sub, Ap.type.table, tt2, tt3, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, w3, hsp_responsive, hsp_all, mh.test, mh_plot, Ap.BP.resultParentChild, resp.stress.responsive.count, T_on.high.ttest, T_on.low.ttest, T_off.int.high.ttest, T_off.int.low.ttest, Ap.gsea.intersect, Ar.int.A22.bim.gsea, Ar.int.A22.low.gsea, Ar.int.A22.lowbim.gsea, quadratic.lms, resp.TPM.dt.sub.pred, md, file = paste("doc/ms_", Sys.Date(), ".RData", sep = ""))

save(sigtable, chi1, chi2, chi3, chi4, chi5, chi6, resp.TPM.dt.sub, Ap.type.table, tt2, tt3, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, w3, hsp_responsive, hsp_all, mh.test, mh_plot, T_on.high.ttest, T_on.low.ttest, T_off.int.high.ttest, T_off.int.low.ttest, Ar.int.A22.bim.gsea, Ar.int.A22.low.gsea, Ar.int.A22.lowbim.gsea, md, file = paste("doc/ms_slim_", Sys.Date(), ".RData", sep = ""))
```
